Code for Submission

### 2023-06-12 CodeForSubmission.Rmd
Changed all labels on graphs to new terminology, etc.

```{r}
library(tidyverse)
library(ggplot2)
library(Rmisc)
library(lubridate)
library(lmerTest)
library(nnet)
library(jmv)
```

@@

dataviolin <- data
dataviolin$fate <- gsub(" mongo", "", dataviolin$fate)
dataviolin$fate <- factor(dataviolin$fate, levels = c("wander", "em", "wowe"))
```

@@

```{r}
violins <- ggplot(data = dataviolin, aes(x = treatment, y = mass.max)) + 
  geom_violin(fill = "light grey", color = "light grey") + 
  geom_jitter(aes(color = fate, shape = food), width = 0.1, height = 0) + 
  theme_bw() + 
  labs(x = "Treatment Group", y  = "Maximum mass achieved (mg)",  color = "Developmental Outcome", shape = "Hostplant") + 
  scale_color_manual(values = c("#1E88E5", "lime green", "#D81B60"), 
                     labels = c("Wander", "WE", "WOWE")) + 
  scale_shape_manual(values = c(1, 19))

@@

```{r}
barsdead <- ggplot(data = datadead, aes(x = treatment, fill = fate)) + 
  theme_bw() + 
  geom_bar(position = "fill") + 
  facet_wrap(~food) + 
  scale_y_continuous(breaks = c(0, .25, .5, .75, 1), limits = c(0, 1.07)) + 
  labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "Developmental Outcome") + 
  scale_fill_manual(values = c("dead" = "purple", "wander" = "#1E88E5" , "em" = "lime green", 
                                       "wowe" = "orange", "wowe mongo" =  "#D81B60"),
                    labels = c("Died", "Wander", "WE", "Small WOWE", "Large WOWE")) + 
  geom_text(data = samplesize, aes(x = x, y = y, label = N))

@@

```{r}
newwaspplot <- ggplot(data = waspmeans, aes(x = stage, y = number, group = comb, color = treatment)) + 
  theme_bw() + 
  geom_line(aes(linetype = food)) + 
  geom_point(aes(shape = food), size = 3) + 
  geom_errorbar(aes(ymin = number - se, ymax = number + se), size = 0.25, width = 0.2) + 
  scale_linetype_manual(values = c("dashed", "solid")) + 
  scale_shape_manual(values = c(1, 19)) + 
  labs(x = "Wasp Developmental Stage", y = "Number of wasps per caterpillar host", shape = "Hostplant", 
       linetype = "Hostplant", color = "Treatment")

@@

@@

```{r}
newarea <- ggplot(data = datalong5, aes(x = area, y = mass.max, color = fate, shape = food)) + 
  theme_bw() + 
  geom_point(alpha = 0.4) + 
  scale_shape_manual(values = c(1, 19)) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
                     labels = c("Wander", "WE", "Small WOWE", "Large WOWE")) + 
  ylim(0, 20) + 
  xlim(0, .6) +
  geom_point(aes(x = area, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5, width = 0) + 
  geom_errorbarh(data = datameans2, aes(xmin = area - arease, xmax = area + arease), size = .5) + 
  guides(size = FALSE) + 
  labs(x = expression(paste("Hostplant leaf area consumed ", (m^{2}))), y = "Maximum mass achieved (g)", 
       shape = "Hostplant Consumed", color = "Developmental Outcome")

>>>>

```{r}
library(tidyverse)
library(ggplot2)
library(Rmisc)
library(lubridate)
library(lmerTest)
library(nnet)
library(jmv)
library(scales)
```

@@

dataviolin <- data
#dataviolin$fate <- gsub(" mongo", "", dataviolin$fate)
#dataviolin$fate <- factor(dataviolin$fate, levels = c("wander", "em", "wowe"))
```

@@

```{r}
violins <- ggplot(data = dataviolin, aes(x = treatment, y = mass.max/1000)) + 
  geom_violin(fill = "light grey", color = "light grey") + 
  geom_jitter(aes(color = fate, shape = food), width = 0.1, height = 0) + 
  theme_bw() + 
  labs(x = "Treatment Group", y  = "Maximum mass achieved (g)",  color = "System Outcome", shape = "Hostplant") + 
  scale_color_manual(values = c("wander" = "#1E88E5" , "em" = "lime green", 
                                       "wowe" = "orange", "wowe mongo" =  "#D81B60"),
                    labels = c("Caterpillar pre-pupation", "Wasp emergence", 
                               "Wasp larval death", "Wasp egg death")) +
  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacco"))

@@

```{r}
barsdead <- ggplot(data = datadead, aes(x = treatment, fill = fate)) + 
  theme_bw() + 
  geom_bar(position = "fill") + 
  facet_wrap(~food) + 
  scale_y_continuous(breaks = c(0, .25, .5, .75, 1), limits = c(0, 1.07)) + 
  labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "System Outcome") + 
  scale_fill_manual(values = c("dead" = "purple", "wander" = "#1E88E5" , "em" = "lime green", 
                                       "wowe" = "orange", "wowe mongo" =  "#D81B60"),
                    labels = c("Died before expt. end", "Caterpillar pre-pupation", "Wasp emergence", 
                               "Wasp larval death", "Wasp egg death")) + 
  geom_text(data = samplesize, aes(x = x, y = y, label = N))

@@

```{r}
newwaspplot <- ggplot(data = waspmeans, aes(x = stage, y = number, group = comb, color = treatment)) + 
  theme_bw() + 
  geom_line(aes(linetype = food)) + 
  geom_point(aes(shape = food), size = 3) + 
  geom_errorbar(aes(ymin = number - se, ymax = number + se), size = 0.25, width = 0.2) + 
  scale_linetype_manual(values = c("dashed", "solid"), labels = c("Devil's claw", "Tobacco")) + 
  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacco")) + 
  scale_color_manual(values = c( "#00BFC4", "#F8766D"), 
                     labels = c("Parasitized non-heat shocked", "Parasitized heat shocked")) + 
  labs(x = "Wasp Developmental Stage", y = "Number of wasps per caterpillar host", shape = "Hostplant", 
       linetype = "Hostplant", color = "Treatment")

@@

```{r}
datalong5$treatment <- factor(datalong5$treatment, labels = c("Non-parasitized non-heat shocked", "Non-parasitized heat shocked", "Parasitized non-heat shocked", "Parasitized heat shocked"))

newmeansfacet <- ggplot(data = datalong5, aes(x = ttmax, y = mass.max, color = fate, shape = food)) + 
  facet_wrap(~ treatment) + 
  theme_bw() + 
  xlim(15, 45) +
  ylim(0, 20) + 
  geom_point(alpha = 0.8) + 
  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacco")) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
                     labels = c("Caterpillar pre-pupation", "Wasp emergence", "Wasp larval death", 
                                "Wasp egg death")) + 
#  geom_point(aes(x = ttmax, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
#  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
#  geom_errorbarh(data = datameans2, aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
#  guides(size = FALSE) + 
  labs(x = "Age at maximum mass (days)", y = "Maximum mass achieved (g)", 
       shape = "Hostplant", color = "System Outcome")

newmeansfacet
```

@@

```{r}
newarea <- ggplot(data = datalong5, aes(x = area, y = mass.max, color = fate, shape = food)) + 
  theme_bw() + 
  geom_point(alpha = 0.4) + 
  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacaco")) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
                     labels = c("Caterpillar pre-pupation", "Wasp emergence", "Wasp larval death", 
                                "Wasp egg death")) + 
  ylim(0, 20) + 
  xlim(0, .6) +
  geom_point(aes(x = area, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5, width = 0) + 
  geom_errorbarh(data = datameans2, aes(xmin = area - arease, xmax = area + arease), size = .5) + 
  guides(size = FALSE) + 
  labs(x = expression(paste("Hostplant leaf area consumed ", (m^{2}))), y = "Maximum mass achieved (g)", 
       shape = "Hostplant", color = "System Outcome")
